---
title: "p8105_hw6_ll3407"
output: github_document
date: "2022-11-25"
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(purrr)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

## Problem 2
Create a city_state variable and a binary variable indicating whether the homicide is solved. 
Omit four cities.
Limit to whites and blacks.
```{r}
homicide = read_csv(file = "./data/homicide-data.csv") %>%
  janitor::clean_names() %>% 
  unite("city_state",c("city", "state"), sep = ",") %>% 
  mutate(
    resolved = recode(
       disposition, 'Closed by arrest' = 1, 'Closed without arrest' = 0, 'Open/No arrest' = 0)) %>% 
  filter(city_state != c("Dallas,TX", "Phoenix,AZ", "Kansas City,MO", "Tulsa,AL")) %>% 
  filter(victim_race == c("White","Black"))%>% 
  mutate(victim_age = as.numeric(victim_age))

```

Fit a logistic regression model for Baltimore
```{r}
Baltimore = homicide %>% 
  filter(city_state == "Baltimore,MD") 

  fit_Baltimore = glm(resolved ~ victim_age + victim_sex + victim_race, data = Baltimore)

```

OR and 95% CIs for the resolved homicide comparing male to female in Baltimore
```{r}
OR_Baltimore = fit_Baltimore %>% broom::tidy() %>%
  filter(term == "victim_sexMale") %>% 
  select(estimate, std.error) %>% 
  mutate(
    OR_M_to_F = exp(estimate),
    ci_lower = exp(estimate-1.96*std.error), 
    ci_upper = exp(estimate+1.96*std.error)
  )
```

GLM for each city.
OR and 95% CI for resolved homicides comparing male to female.
```{r}
nest = homicide %>% 
  select(city_state,resolved,victim_age,victim_sex,victim_race) %>% 
  mutate(race = recode(
       victim_race, 'Black' = 1, 'White' = 0)) %>%   mutate(sex_male = recode(
       victim_sex, 'Male' = 1, 'Female' = 0, 'Unknown' = 0)) %>% 
   mutate(sex_unknown = recode(
       victim_sex, 'Unknown' = 1, 'Female' = 0, 'Male' = 0))  %>% 
  nest(df = -city_state) 

OR = nest %>% 
  mutate(
    models = map(.x = df, ~lm(resolved ~ victim_age + sex_male + sex_unknown + race , data = .x )),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state,results) %>% 
  unnest(results) 
  
  OR_all = OR%>%
  filter(term == "sex_male") %>% 
  select(city_state, estimate, std.error) %>% 
  mutate(
    OR_M_to_F = exp(estimate),
    ci_lower = exp(estimate-1.96*std.error), 
    ci_upper = exp(estimate+1.96*std.error)
  ) %>% 
    select( -estimate, -std.error) 
```

Plot of ORs and CIs for each city.
```{r}
plot_OR = OR_all %>% ggplot(aes(reorder(city_state,OR_M_to_F), y = OR_M_to_F)) + geom_point() + 
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper))+ 
  labs(
    title = "Plot of Plot of ORs and CIs for resolved homicides comparing male to female in each city",
    x = "City",
    y = "OR and 95% CIs") +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5, hjust = 1))

plot_OR


```
Comment: Telsa in AL has the highest OR of resolved homicides comparing males to females, while New York in NY has the lowest. San Bernardino in CA has the widest CI range of resolved homicides comparing males to females, while Chicago in IL has the narrowest.

## Problem 3
Read and clean data
```{r}
BW = read_csv(file = "./data/birthweight.csv") %>%
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex)) %>% 
  mutate(frace = as.factor(frace)) %>% 
  mutate(malform = as.factor(malform)) %>% 
  mutate(mrace = as.factor(mrace)) 

head(BW, 100)
```

Check missing data

```{r}
  summary(BW$pnumlbw)
  summary(BW$pnumsga)
  
```

Variables of pnumlbw and pnumsga are with "0" value, so we should not include them in the models 
```{r}
fit_BW = 
  BW %>% lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + ppbmi + ppwt + smoken + wtgain, data = .) %>% broom::tidy()  
  
exclude = fit_BW %>% filter(p.value >= 0.05)
view(exclude)

```

In the logistic models, we will remove the covariate with a p-value>=0.05 (fincome, frace, malforml, menarche, mheight, momage, ppbmi, ppwt).

```{r}
lm_BW = lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + parity + smoken + wtgain, data = BW) %>% broom::tidy()
```


